Poisson Regression

### 2019-12-13 rmds/poisson_regression.Rmd
first attempt at bayesian lasso - not working yet

y <- mod_dat$daily_boards
E <- mod_dat$daily_stops

N <- nrow(mod_dat)

K <- 4
x <- matrix(ncol = 4, c(mod_dat$pop_density, mod_dat$emp_density, mod_dat$perc_no_veh, mod_dat$walkability))

@@

```{r}
poisson_theta <- "/Users/raven/Documents/honors/honors-project/stan/poisson_theta.stan"

#poisson_theta_fit <- stan(poisson_theta, data = standat1, warmup = 1000, iter = 2000)
#saveRDS(poisson_theta_fit, "/Users/raven/Documents/honors/honors-project/fits/poisson_theta_test.RDS")

@@

launch_shinystan(poisson_theta_fit)
```

>>>>

xdat <- mod_dat[, -c("GEOID", "daily_boards_per_stop", "sqkm", "perc_transit_comm")] # still need to fix that var
xdat <- na.omit(xdat)

y <- xdat$daily_boards
E <- xdat$daily_stops

N <- nrow(xdat)

K <- 27
x <- as.matrix(xdat)

@@

```{r}
poisson_theta <- "/Users/mcknigri/Documents/honors/honors-project/stan/poisson_theta.stan"

poisson_theta_fit_LASSO <- stan(poisson_theta, data = standat1, warmup = 7000, iter = 8000)
#saveRDS(poisson_theta_fit, "/Users/raven/Documents/honors/honors-project/fits/poisson_theta_test.RDS")

@@

launch_shinystan(poisson_theta_fit_LASSO)
```
